Analysis of pudding following Davidson 1970

### 2021-11-05 inst/pudding.Rmd
description of return value of convert()

This short document creates the `pudding` suite of R objects and
presents some preliminary analysis.  It follows Davidson 1970 and the
`PlackettLuce` package.

@@

Here is a method to convert the pudding matrix to a likelihood function:

```{r,cache=TRUE}

    numbers <- as.character(1:6)
    puddings <- paste("pudding",numbers,sep="_")
    tyers    <- paste("tie",numbers,sep="_")

@@

@@

>>>>

This short document creates the `pudding` suite of R objects and
presents some preliminary analysis.  It is not particularly
well-structured or terse and is essentially a sequence of notes.  It
follows Davidson 1970 and the `PlackettLuce` package.

@@

Here is a method to convert the pudding matrix to a `hyper2`
likelihood function:

```{r,cache=TRUE}
numbers <- as.character(1:6)
puddings <- paste("pudding",numbers,sep="_")
tyers    <- paste("tie",numbers,sep="_")

@@

Function `convert()` gives a list of three `hyper2` objects.  The
first assumes that each pudding has a strength $p_i$, $1\leq i\leq 6$
and

\[
\operatorname{Prob}(i\succ j) = \frac{\pi_i}{\pi_i+\pi_j+D}\\
\operatorname{Prob}(j\succ i) = \frac{\pi_j}{\pi_i+\pi_j+D}\\
\operatorname{Prob}(i\sim  j) = \frac{D}{\pi_i+\pi_j+D}
\]

where $p_i,D\geq 0$ and $\sum p_i+D=1$ (here $i\succ j$ means $i$ is
preferred to $j$ and $i\sim j$ means no preference).  The second
element is a generalization of the first, allowing the tying
propensities to differ:

\[
\operatorname{Prob}(i\succ j) = \frac{\pi_i}{\pi_i+\pi_j+D_i+D_j}\\
\operatorname{Prob}(j\succ i) = \frac{\pi_j}{\pi_i+\pi_j+D_i+D_j}\\
\operatorname{Prob}(i\sim  j) = \frac{D}{\pi_i+\pi_j+D_i+D_j}
\]

where $\sum p_i+D_i=1$.  The third element is a generalization of the
second, giving the first pudding a "first-mover" advantage analogous
to the home-team advantage in football, or playing white in chess:

@@

\[
\operatorname{Prob}(i\succ j) = \frac{\pi_i+F}{\pi_i+\pi_j+D_i+D_j+F}\\
\operatorname{Prob}(j\succ i) = \frac{\pi_j}{\pi_i+\pi_j+D_i+D_j+F}\\
\operatorname{Prob}(i\sim  j) = \frac{D}{\pi_i+\pi_j+D_i+D_j+F}
\]

Above, the first-mover advantage is given to pudding $i$.  We can use
these now:
